---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}
@import url('https://fonts.googleapis.com/css2?family=Roboto+Slab:wght@100..900&display=swap');

body {
  font-family: 'Roboto Slab';
  padding:10px
}
```

## Dynamic Report of Steam's Recommended Games

*An analysis of the "Steam Recommended Page" data currently recorded in Google Sheets*

---

```{r}
library(tidyverse)

logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vSNgQgD-2uGRVZMrgSd7WZ8fKjyIfZf-9nLJmLmfoGfkl63MTWI6czrAT56rloVPRysxuMrkLk9__fl/pub?output=csv")

latest_data <- logged_data %>% 
  rename(
      name = 2,
      single_or_multi = 3,
      genres = 4,
      price = 5
      ) %>%
  separate_rows(genres, sep = ", ")

highest_price <- max(latest_data$price)

lowest_price <- min(latest_data$price)

mean_price <- mean(latest_data$price) %>% round(2)

mean_name_length <- nchar(latest_data$name) %>% mean() %>% round()

entries_count <- nrow(logged_data)

genre_plot <- ggplot(data = latest_data) +
  geom_bar(aes(x = genres, fill =), fill = "#4f95f0") +
  labs(title = "Guns or roses?",
       subtitle = "Comparing the counts of each genre across all recommendations",
       caption = "(Data updated dynamically through Google Forms)",
       x = "Game Genres",
       y = "Number of Occurrences")

playstyle_plot <- ggplot(data = latest_data) +
  geom_bar(aes(x = single_or_multi), fill = "#231370") +
  labs(title = "The more the merrier?",
       subtitle = "Comparing how often multiplayer and singleplayer games were each recommended",
       caption = "(Data updated dynamically through Google Forms)",
       x = "Playstyle",
       y = "Number of Recommendations")

```

### Recommendations for Multiplayer Vs. Singleplayer Games

```{r}
playstyle_plot
```

### Most Frequently Occuring Genres Across All Recommendations

```{r}
genre_plot
```

---

### Additional Summaries

Given the `r entries_count` *currently recorded* entries of recommended games, we can also
gather the following:

- The highest price is recorded at NZD$`r highest_price`.
- The lowest price is recorded at NZD$`r lowest_price`.
- The mean price, across all current entries, is recorded at NZD$`r mean_price`.
- The mean title length is, on average, `r mean_name_length` characters long.

